Manuscript title here

### 2024-09-17 manuscript.Rmd
la till 2 källor

The initial management of trauma patients once they reach hospital is very time sensitive and error prone [@mackersie_pitfalls_2010].

>>>>

The initial management of trauma patients once they reach hospital is very time sensitive and error prone [@mackersie_pitfalls_2010][@teixeira_preventable_2007][@ivatury_patient_2008].
